Analyzing the Privacy Paradox Using a Nationally Representative Three-Wave Panel Study

### 2020-10-22 analyses.Rmd
- thorough update for 2. revision

```{r Packages, cache=F, results='hide'}
# relevant packages
devtools::install_github("tdienlin/td@v.0.0.2.5")
required <- c("GGally", "ggplot2", "kableExtra", "knitr",
              "lavaan", "lme4","magrittr", "MissMech", 
              "papaja", "psych", "pwr", "MVN", "semTools", 
              "sjstats", "tidyverse", "td")

@@

corr_plot <- ggpairs(d_fs,
                     lower = list(continuous = wrap(td::scat_plot, coords = c(1, 5, 1, 5)))) + 
  theme_bw()
print(corr_plot)
```

>>>>

```{r Packages, cache=F, results='hide'}
# relevant packages
devtools::install_github("tdienlin/td@v0.0.2.6")
required <- c("GGally", "ggplot2", "kableExtra", "knitr",
              "lavaan", "lme4","magrittr", "MissMech", 
              "papaja", "psych", "pwr", "MVN", "semTools", 
              "sjstats", "tidyverse", "td")

@@

corr_plot <- ggpairs(d_fs,
                     upper = list(continuous = cor_plot),
                     lower = list(continuous = wrap(td::scat_plot, coords = c(1, 5, 1, 5)))) + 
  theme_bw()
print(corr_plot)
```

### 2020-10-22 analyses_additional.Rmd
- thorough update for 2. revision

---
title: "Analyzing the Privacy Paradox Using a Nationally Representative Three-Wave Panel Study"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    df_print: paged
    code_folding: hide
---

@@

```{r Packages, cache=F, results='hide'}
# relevant packages
devtools::install_github("tdienlin/td@v.0.0.2.5")
required <- c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
              "MissMech", "papaja", "psych", "pwr", "MVN", "semTools", 
              "sjstats", "tidyverse", "td")

@@

```{r CFA_All}
name <- "all_vars"
no <- 0
model <- '
# Privacy Concerns
# create factors
t1_pri_con_f =~ 1*t1_pri_con_f1 + a2*t1_pri_con_f2
t2_pri_con_f =~ 1*t2_pri_con_f1 + a2*t2_pri_con_f2
t3_pri_con_f =~ 1*t3_pri_con_f1 + a2*t3_pri_con_f2
t1_pri_con_f1 =~ 1*t1_pri_con_04 + b2*t1_pri_con_05 + b3*t1_pri_con_06
t1_pri_con_f2 =~ 1*t1_pri_con_07 + c2*t1_pri_con_08 + c3*t1_pri_con_09
t2_pri_con_f1 =~ 1*t2_pri_con_04 + b2*t2_pri_con_05 + b3*t2_pri_con_06
t2_pri_con_f2 =~ 1*t2_pri_con_07 + c2*t2_pri_con_08 + c3*t2_pri_con_09
t3_pri_con_f1 =~ 1*t3_pri_con_04 + b2*t3_pri_con_05 + b3*t3_pri_con_06
t3_pri_con_f2 =~ 1*t3_pri_con_07 + c2*t3_pri_con_08 + c3*t3_pri_con_09

@@

>>>>

---
title: "Analyzing the Privacy Paradox Using a Nationally Representative Three-Wave Panel Study"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    df_print: paged
    code_folding: hide
    number_sections: true
---

@@

```{r Packages, cache=F, results='hide'}
# relevant packages
devtools::install_github("tdienlin/td@v0.0.2.6")
required <- c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
              "MissMech", # attention: pkg is obsolete, needs to be installed manually
              "papaja", "psych", "pwr", "MVN", "semTools", 
              "sjstats", "tidyverse", "td")

@@

```{r CFA_All_ALL}
name <- "all_vars"
no <- 0
model <- '
# Privacy Concerns
# create factors
t1_pri_con_f =~ 1*t1_pri_con_f1 + a2*t1_pri_con_f2
t2_pri_con_f =~ 1*t2_pri_con_f1 + a2*t2_pri_con_f2
t3_pri_con_f =~ 1*t3_pri_con_f1 + a2*t3_pri_con_f2
t1_pri_con_f1 =~ 1*t1_pri_con_04 + b2*t1_pri_con_05 + b3*t1_pri_con_06
t1_pri_con_f2 =~ 1*t1_pri_con_07 + c2*t1_pri_con_08 + c3*t1_pri_con_09
t2_pri_con_f1 =~ 1*t2_pri_con_04 + b2*t2_pri_con_05 + b3*t2_pri_con_06
t2_pri_con_f2 =~ 1*t2_pri_con_07 + c2*t2_pri_con_08 + c3*t2_pri_con_09
t3_pri_con_f1 =~ 1*t3_pri_con_04 + b2*t3_pri_con_05 + b3*t3_pri_con_06
t3_pri_con_f2 =~ 1*t3_pri_con_07 + c2*t3_pri_con_08 + c3*t3_pri_con_09

@@

#### Model 7 (longer intervals)

This is like the final model reported in the paper, but with other, that is longer, intervals. Now, waves are separated by 1 year and span until 2018.

We first need to redo the factor scores, because we now have a different sample.

Specifically, we first estimate a model containing all measures, which is then used to extract factor scores.

```{r CFA_All}
name <- "all_vars"
model <- '
# Privacy Concerns
# create factors
t1_pri_con_f =~ 1*t1_pri_con_f1 + a2*t1_pri_con_f2
t3_pri_con_f =~ 1*t3_pri_con_f1 + a2*t3_pri_con_f2
t4_pri_con_f =~ 1*t4_pri_con_f1 + a2*t4_pri_con_f2
t5_pri_con_f =~ 1*t5_pri_con_f1 + a2*t5_pri_con_f2
t1_pri_con_f1 =~ 1*t1_pri_con_04 + b2*t1_pri_con_05 + b3*t1_pri_con_06
t1_pri_con_f2 =~ 1*t1_pri_con_07 + c2*t1_pri_con_08 + c3*t1_pri_con_09
t3_pri_con_f1 =~ 1*t3_pri_con_04 + b2*t3_pri_con_05 + b3*t3_pri_con_06
t3_pri_con_f2 =~ 1*t3_pri_con_07 + c2*t3_pri_con_08 + c3*t3_pri_con_09
t4_pri_con_f1 =~ 1*t4_pri_con_04 + b2*t4_pri_con_05 + b3*t4_pri_con_06
t4_pri_con_f2 =~ 1*t4_pri_con_07 + c2*t4_pri_con_08 + c3*t4_pri_con_09
t5_pri_con_f1 =~ 1*t5_pri_con_04 + b2*t5_pri_con_05 + b3*t5_pri_con_06
t5_pri_con_f2 =~ 1*t5_pri_con_07 + c2*t5_pri_con_08 + c3*t5_pri_con_09

# error covariances
t5_pri_con_04 ~~ t4_pri_con_04 + t3_pri_con_04 + t1_pri_con_04
t5_pri_con_05 ~~ t4_pri_con_05 + t3_pri_con_05 + t1_pri_con_05
t5_pri_con_06 ~~ t4_pri_con_06 + t3_pri_con_06 + t1_pri_con_06
t5_pri_con_07 ~~ t4_pri_con_07 + t3_pri_con_07 + t1_pri_con_07
t5_pri_con_08 ~~ t4_pri_con_08 + t3_pri_con_08 + t1_pri_con_08
t5_pri_con_09 ~~ t4_pri_con_09 + t3_pri_con_09 + t1_pri_con_09
t4_pri_con_04 ~~ t3_pri_con_04 + t1_pri_con_04
t4_pri_con_05 ~~ t3_pri_con_05 + t1_pri_con_05
t4_pri_con_06 ~~ t3_pri_con_06 + t1_pri_con_06
t4_pri_con_07 ~~ t3_pri_con_07 + t1_pri_con_07
t4_pri_con_08 ~~ t3_pri_con_08 + t1_pri_con_08
t4_pri_con_09 ~~ t3_pri_con_09 + t1_pri_con_09
t3_pri_con_04 ~~ t1_pri_con_04
t3_pri_con_05 ~~ t1_pri_con_05 
t3_pri_con_06 ~~ t1_pri_con_06
t3_pri_con_07 ~~ t1_pri_con_07
t3_pri_con_08 ~~ t1_pri_con_08
t3_pri_con_09 ~~ t1_pri_con_09

# factor covariances
t5_pri_con_f ~~ t1_pri_con_f + t3_pri_con_f + t4_pri_con_f
t1_pri_con_f ~~ t3_pri_con_f + t4_pri_con_f
t3_pri_con_f ~~ t4_pri_con_f

# Information Sharing Attitude
# create factors
t1_inf_sha_att_f =~ 1*t1_inf_sha_att_f1 + d2*t1_inf_sha_att_f2 + d3*t1_inf_sha_att_f3 + d4*t1_inf_sha_att_f4 + d5*t1_inf_sha_att_f5
t3_inf_sha_att_f =~ 1*t3_inf_sha_att_f1 + d2*t3_inf_sha_att_f2 + d3*t3_inf_sha_att_f3 + d4*t3_inf_sha_att_f4 + d5*t3_inf_sha_att_f5
t4_inf_sha_att_f =~ 1*t4_inf_sha_att_f1 + d2*t4_inf_sha_att_f2 + d3*t4_inf_sha_att_f3 + d4*t4_inf_sha_att_f4 + d5*t4_inf_sha_att_f5
t5_inf_sha_att_f =~ 1*t5_inf_sha_att_f1 + d2*t5_inf_sha_att_f2 + d3*t5_inf_sha_att_f3 + d4*t5_inf_sha_att_f4 + d5*t5_inf_sha_att_f5

t1_inf_sha_att_f1 =~ 1*t1_inf_sha_att_01 + e*t1_inf_sha_att_02
t1_inf_sha_att_f2 =~ 1*t1_inf_sha_att_03 + f*t1_inf_sha_att_04
t1_inf_sha_att_f3 =~ 1*t1_inf_sha_att_05 + g*t1_inf_sha_att_06
t1_inf_sha_att_f4 =~ 1*t1_inf_sha_att_07 + h*t1_inf_sha_att_08
t1_inf_sha_att_f5 =~ 1*t1_inf_sha_att_10 + i*t1_inf_sha_att_11
t3_inf_sha_att_f1 =~ 1*t3_inf_sha_att_01 + e*t3_inf_sha_att_02
t3_inf_sha_att_f2 =~ 1*t3_inf_sha_att_03 + f*t3_inf_sha_att_04
t3_inf_sha_att_f3 =~ 1*t3_inf_sha_att_05 + g*t3_inf_sha_att_06
t3_inf_sha_att_f4 =~ 1*t3_inf_sha_att_07 + h*t3_inf_sha_att_08
t3_inf_sha_att_f5 =~ 1*t3_inf_sha_att_10 + i*t3_inf_sha_att_11
t4_inf_sha_att_f1 =~ 1*t4_inf_sha_att_01 + e*t4_inf_sha_att_02
t4_inf_sha_att_f2 =~ 1*t4_inf_sha_att_03 + f*t4_inf_sha_att_04
t4_inf_sha_att_f3 =~ 1*t4_inf_sha_att_05 + g*t4_inf_sha_att_06
t4_inf_sha_att_f4 =~ 1*t4_inf_sha_att_07 + h*t4_inf_sha_att_08
t4_inf_sha_att_f5 =~ 1*t4_inf_sha_att_10 + i*t4_inf_sha_att_11
t5_inf_sha_att_f1 =~ 1*t5_inf_sha_att_01 + e*t5_inf_sha_att_02
t5_inf_sha_att_f2 =~ 1*t5_inf_sha_att_03 + f*t5_inf_sha_att_04
t5_inf_sha_att_f3 =~ 1*t5_inf_sha_att_05 + g*t5_inf_sha_att_06
t5_inf_sha_att_f4 =~ 1*t5_inf_sha_att_07 + h*t5_inf_sha_att_08
t5_inf_sha_att_f5 =~ 1*t5_inf_sha_att_10 + i*t5_inf_sha_att_11

# factor covariance
t5_inf_sha_att_f ~~ t1_inf_sha_att_f + t3_inf_sha_att_f + t4_inf_sha_att_f
t1_inf_sha_att_f ~~ t3_inf_sha_att_f + t4_inf_sha_att_f
t3_inf_sha_att_f ~~ t4_inf_sha_att_f

# item error covariance
t5_inf_sha_att_01 ~~ t1_inf_sha_att_01 + t3_inf_sha_att_01 + t4_inf_sha_att_01
t1_inf_sha_att_01 ~~ t3_inf_sha_att_01 + t4_inf_sha_att_01
t3_inf_sha_att_01 ~~ t4_inf_sha_att_01
t5_inf_sha_att_02 ~~ t1_inf_sha_att_02 + t3_inf_sha_att_02 + t4_inf_sha_att_02
t1_inf_sha_att_02 ~~ t3_inf_sha_att_02 + t4_inf_sha_att_02
t3_inf_sha_att_02 ~~ t4_inf_sha_att_02
t5_inf_sha_att_03 ~~ t1_inf_sha_att_03 + t3_inf_sha_att_03 + t4_inf_sha_att_03
t1_inf_sha_att_03 ~~ t3_inf_sha_att_03 + t4_inf_sha_att_03
t3_inf_sha_att_03 ~~ t4_inf_sha_att_03
t5_inf_sha_att_04 ~~ t1_inf_sha_att_04 + t3_inf_sha_att_04 + t4_inf_sha_att_04
t1_inf_sha_att_04 ~~ t3_inf_sha_att_04 + t4_inf_sha_att_04
t3_inf_sha_att_04 ~~ t4_inf_sha_att_04
t5_inf_sha_att_05 ~~ t1_inf_sha_att_05 + t3_inf_sha_att_05 + t4_inf_sha_att_05
t1_inf_sha_att_05 ~~ t3_inf_sha_att_05 + t4_inf_sha_att_05
t3_inf_sha_att_05 ~~ t4_inf_sha_att_05
t5_inf_sha_att_06 ~~ t1_inf_sha_att_06 + t3_inf_sha_att_06 + t4_inf_sha_att_06
t1_inf_sha_att_06 ~~ t3_inf_sha_att_06 + t4_inf_sha_att_06
t3_inf_sha_att_06 ~~ t4_inf_sha_att_06
t5_inf_sha_att_07 ~~ t1_inf_sha_att_07 + t3_inf_sha_att_07 + t4_inf_sha_att_07
t1_inf_sha_att_07 ~~ t3_inf_sha_att_07 + t4_inf_sha_att_07
t3_inf_sha_att_07 ~~ t4_inf_sha_att_07
t5_inf_sha_att_08 ~~ t1_inf_sha_att_08 + t3_inf_sha_att_08 + t4_inf_sha_att_08
t1_inf_sha_att_08 ~~ t3_inf_sha_att_08 + t4_inf_sha_att_08
t3_inf_sha_att_08 ~~ t4_inf_sha_att_08
t5_inf_sha_att_10 ~~ t1_inf_sha_att_10 + t3_inf_sha_att_10 + t4_inf_sha_att_10
t1_inf_sha_att_10 ~~ t3_inf_sha_att_10 + t4_inf_sha_att_10
t3_inf_sha_att_10 ~~ t4_inf_sha_att_10
t5_inf_sha_att_11 ~~ t1_inf_sha_att_11 + t3_inf_sha_att_11 + t4_inf_sha_att_11
t1_inf_sha_att_11 ~~ t3_inf_sha_att_11 + t4_inf_sha_att_11
t3_inf_sha_att_11 ~~ t4_inf_sha_att_11

# information sharing behavior
# create factors
t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_f1 + o2*t1_inf_sha_beh_f2 + o3*t1_inf_sha_beh_f3 + o4*t1_inf_sha_beh_f4 + o5*t1_inf_sha_beh_f5
t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_f1 + o2*t3_inf_sha_beh_f2 + o3*t3_inf_sha_beh_f3 + o4*t3_inf_sha_beh_f4 + o5*t3_inf_sha_beh_f5
t4_inf_sha_beh_f =~ 1*t4_inf_sha_beh_f1 + o2*t4_inf_sha_beh_f2 + o3*t4_inf_sha_beh_f3 + o4*t4_inf_sha_beh_f4 + o5*t4_inf_sha_beh_f5
t5_inf_sha_beh_f =~ 1*t5_inf_sha_beh_f1 + o2*t5_inf_sha_beh_f2 + o3*t5_inf_sha_beh_f3 + o4*t5_inf_sha_beh_f4 + o5*t5_inf_sha_beh_f5
t1_inf_sha_beh_f1 =~ 1*t1_inf_sha_beh_01 + j2*t1_inf_sha_beh_02
t1_inf_sha_beh_f2 =~ 1*t1_inf_sha_beh_03 + k2*t1_inf_sha_beh_04
t1_inf_sha_beh_f3 =~ 1*t1_inf_sha_beh_05 + l2*t1_inf_sha_beh_06
t1_inf_sha_beh_f4 =~ 1*t1_inf_sha_beh_07 + m2*t1_inf_sha_beh_08
t1_inf_sha_beh_f5 =~ 1*t1_inf_sha_beh_10 + n2*t1_inf_sha_beh_11
t3_inf_sha_beh_f1 =~ 1*t3_inf_sha_beh_01 + j2*t3_inf_sha_beh_02
t3_inf_sha_beh_f2 =~ 1*t3_inf_sha_beh_03 + k2*t3_inf_sha_beh_04
t3_inf_sha_beh_f3 =~ 1*t3_inf_sha_beh_05 + l2*t3_inf_sha_beh_06
t3_inf_sha_beh_f4 =~ 1*t3_inf_sha_beh_07 + m2*t3_inf_sha_beh_08
t3_inf_sha_beh_f5 =~ 1*t3_inf_sha_beh_10 + n2*t3_inf_sha_beh_11
t4_inf_sha_beh_f1 =~ 1*t4_inf_sha_beh_01 + j2*t4_inf_sha_beh_02
t4_inf_sha_beh_f2 =~ 1*t4_inf_sha_beh_03 + k2*t4_inf_sha_beh_04
t4_inf_sha_beh_f3 =~ 1*t4_inf_sha_beh_05 + l2*t4_inf_sha_beh_06
t4_inf_sha_beh_f4 =~ 1*t4_inf_sha_beh_07 + m2*t4_inf_sha_beh_08
t4_inf_sha_beh_f5 =~ 1*t4_inf_sha_beh_10 + n2*t4_inf_sha_beh_11
t5_inf_sha_beh_f1 =~ 1*t5_inf_sha_beh_01 + j2*t5_inf_sha_beh_02
t5_inf_sha_beh_f2 =~ 1*t5_inf_sha_beh_03 + k2*t5_inf_sha_beh_04
t5_inf_sha_beh_f3 =~ 1*t5_inf_sha_beh_05 + l2*t5_inf_sha_beh_06
t5_inf_sha_beh_f4 =~ 1*t5_inf_sha_beh_07 + m2*t5_inf_sha_beh_08
t5_inf_sha_beh_f5 =~ 1*t5_inf_sha_beh_10 + n2*t5_inf_sha_beh_11

# factor covariance
t5_inf_sha_beh_f ~~ t1_inf_sha_beh_f + t3_inf_sha_beh_f + t4_inf_sha_beh_f
t1_inf_sha_beh_f ~~ t3_inf_sha_beh_f + t4_inf_sha_beh_f
t3_inf_sha_beh_f ~~ t4_inf_sha_beh_f

# item error covariance
t5_inf_sha_beh_01 ~~ t1_inf_sha_beh_01 + t3_inf_sha_beh_01 + t4_inf_sha_beh_01
t1_inf_sha_beh_01 ~~ t3_inf_sha_beh_01 + t4_inf_sha_beh_01
t3_inf_sha_beh_01 ~~ t4_inf_sha_beh_01
t5_inf_sha_beh_02 ~~ t1_inf_sha_beh_02 + t3_inf_sha_beh_02 + t4_inf_sha_beh_02
t1_inf_sha_beh_02 ~~ t3_inf_sha_beh_02 + t4_inf_sha_beh_02
t3_inf_sha_beh_02 ~~ t4_inf_sha_beh_02
t5_inf_sha_beh_03 ~~ t1_inf_sha_beh_03 + t3_inf_sha_beh_03 + t4_inf_sha_beh_03
t1_inf_sha_beh_03 ~~ t3_inf_sha_beh_03 + t4_inf_sha_beh_03
t3_inf_sha_beh_03 ~~ t4_inf_sha_beh_03
t5_inf_sha_beh_04 ~~ t1_inf_sha_beh_04 + t3_inf_sha_beh_04 + t4_inf_sha_beh_04
t1_inf_sha_beh_04 ~~ t3_inf_sha_beh_04 + t4_inf_sha_beh_04
t3_inf_sha_beh_04 ~~ t4_inf_sha_beh_04
t5_inf_sha_beh_05 ~~ t1_inf_sha_beh_05 + t3_inf_sha_beh_05 + t4_inf_sha_beh_05
t1_inf_sha_beh_05 ~~ t3_inf_sha_beh_05 + t4_inf_sha_beh_05
t3_inf_sha_beh_05 ~~ t4_inf_sha_beh_05
t5_inf_sha_beh_06 ~~ t1_inf_sha_beh_06 + t3_inf_sha_beh_06 + t4_inf_sha_beh_06
t1_inf_sha_beh_06 ~~ t3_inf_sha_beh_06 + t4_inf_sha_beh_06
t3_inf_sha_beh_06 ~~ t4_inf_sha_beh_06
t5_inf_sha_beh_07 ~~ t1_inf_sha_beh_07 + t3_inf_sha_beh_07 + t4_inf_sha_beh_07
t1_inf_sha_beh_07 ~~ t3_inf_sha_beh_07 + t4_inf_sha_beh_07
t3_inf_sha_beh_07 ~~ t4_inf_sha_beh_07
t5_inf_sha_beh_08 ~~ t1_inf_sha_beh_08 + t3_inf_sha_beh_08 + t4_inf_sha_beh_08
t1_inf_sha_beh_08 ~~ t3_inf_sha_beh_08 + t4_inf_sha_beh_08
t3_inf_sha_beh_08 ~~ t4_inf_sha_beh_08
t5_inf_sha_beh_10 ~~ t1_inf_sha_beh_10 + t3_inf_sha_beh_10 + t4_inf_sha_beh_10
t1_inf_sha_beh_10 ~~ t3_inf_sha_beh_10 + t4_inf_sha_beh_10
t3_inf_sha_beh_10 ~~ t4_inf_sha_beh_10
t5_inf_sha_beh_11 ~~ t1_inf_sha_beh_11 + t3_inf_sha_beh_11 + t4_inf_sha_beh_11
t1_inf_sha_beh_11 ~~ t3_inf_sha_beh_11 + t4_inf_sha_beh_11
t3_inf_sha_beh_11 ~~ t4_inf_sha_beh_11

## Correlations Attitude and Behavior-Items
t1_inf_sha_beh_01 ~~ t1_inf_sha_att_01
t1_inf_sha_beh_02 ~~ t1_inf_sha_att_02
t1_inf_sha_beh_03 ~~ t1_inf_sha_att_03
t1_inf_sha_beh_04 ~~ t1_inf_sha_att_04
t1_inf_sha_beh_05 ~~ t1_inf_sha_att_05
t1_inf_sha_beh_06 ~~ t1_inf_sha_att_06
t1_inf_sha_beh_07 ~~ t1_inf_sha_att_07
t1_inf_sha_beh_08 ~~ t1_inf_sha_att_08
t1_inf_sha_beh_10 ~~ t1_inf_sha_att_10
t1_inf_sha_beh_11 ~~ t1_inf_sha_att_11
t3_inf_sha_beh_01 ~~ t3_inf_sha_att_01
t3_inf_sha_beh_02 ~~ t3_inf_sha_att_02
t3_inf_sha_beh_03 ~~ t3_inf_sha_att_03
t3_inf_sha_beh_04 ~~ t3_inf_sha_att_04
t3_inf_sha_beh_05 ~~ t3_inf_sha_att_05
t3_inf_sha_beh_06 ~~ t3_inf_sha_att_06
t3_inf_sha_beh_07 ~~ t3_inf_sha_att_07
t3_inf_sha_beh_08 ~~ t3_inf_sha_att_08
t3_inf_sha_beh_10 ~~ t3_inf_sha_att_10
t3_inf_sha_beh_11 ~~ t3_inf_sha_att_11
t4_inf_sha_beh_01 ~~ t4_inf_sha_att_01
t4_inf_sha_beh_02 ~~ t4_inf_sha_att_02
t4_inf_sha_beh_03 ~~ t4_inf_sha_att_03
t4_inf_sha_beh_04 ~~ t4_inf_sha_att_04
t4_inf_sha_beh_05 ~~ t4_inf_sha_att_05
t4_inf_sha_beh_06 ~~ t4_inf_sha_att_06
t4_inf_sha_beh_07 ~~ t4_inf_sha_att_07
t4_inf_sha_beh_08 ~~ t4_inf_sha_att_08
t4_inf_sha_beh_10 ~~ t4_inf_sha_att_10
t4_inf_sha_beh_11 ~~ t4_inf_sha_att_11
t5_inf_sha_beh_01 ~~ t5_inf_sha_att_01
t5_inf_sha_beh_02 ~~ t5_inf_sha_att_02
t5_inf_sha_beh_03 ~~ t5_inf_sha_att_03
t5_inf_sha_beh_04 ~~ t5_inf_sha_att_04
t5_inf_sha_beh_05 ~~ t5_inf_sha_att_05
t5_inf_sha_beh_06 ~~ t5_inf_sha_att_06
t5_inf_sha_beh_07 ~~ t5_inf_sha_att_07
t5_inf_sha_beh_08 ~~ t5_inf_sha_att_08
t5_inf_sha_beh_10 ~~ t5_inf_sha_att_10
t5_inf_sha_beh_11 ~~ t5_inf_sha_att_11
'
assign(paste("fit", name, sep = "_"), cfa(model, d_wide_all, missing = "ML"))
summary(get(paste("fit", name, sep = "_")), standardized = TRUE, fit.measures = TRUE)
```

Extract factor scores.

```{r}
d_fs_all <- lavPredict(get(paste("fit", name, sep = "_")), type = "ov") %>% 
  as.data.frame() %>% 
  mutate(t1_pri_con_fs = rowMeans(select(., starts_with("t1_pri"))),
         t3_pri_con_fs = rowMeans(select(., starts_with("t3_pri"))),
         t4_pri_con_fs = rowMeans(select(., starts_with("t4_pri"))),
         t5_pri_con_fs = rowMeans(select(., starts_with("t5_pri"))),
         t1_inf_sha_att_fs = rowMeans(select(., starts_with("t1_inf_sha_att"))),
         t3_inf_sha_att_fs = rowMeans(select(., starts_with("t3_inf_sha_att"))),
         t4_inf_sha_att_fs = rowMeans(select(., starts_with("t4_inf_sha_att"))),
         t5_inf_sha_att_fs = rowMeans(select(., starts_with("t5_inf_sha_att"))),
         t1_inf_sha_beh_fs = rowMeans(select(., starts_with("t1_inf_sha_beh"))),
         t3_inf_sha_beh_fs = rowMeans(select(., starts_with("t3_inf_sha_beh"))),
         t4_inf_sha_beh_fs = rowMeans(select(., starts_with("t4_inf_sha_beh"))),
         t5_inf_sha_beh_fs = rowMeans(select(., starts_with("t5_inf_sha_beh")))
         ) %>% 
  select(contains("_fs"))
d_wide_all <- cbind(d_fs_all, d_wide_all)
```

Run new model.

```{r}
model <- '
# between relations
pri_con_b =~ 1*t1_pri_con_fs + 1*t3_pri_con_fs + 1*t4_pri_con_fs + 1*t5_pri_con_fs
inf_sha_beh_b =~ 1*t1_inf_sha_beh_fs + 1*t3_inf_sha_beh_fs + 1*t4_inf_sha_beh_fs  + 1*t5_inf_sha_beh_fs
inf_sha_att_b =~ 1*t1_inf_sha_att_fs + 1*t3_inf_sha_att_fs + 1*t4_inf_sha_att_fs + 1*t5_inf_sha_att_fs

# within person changes
t1_pri_con_w =~ 1*t1_pri_con_fs
t3_pri_con_w =~ 1*t3_pri_con_fs
t4_pri_con_w =~ 1*t4_pri_con_fs
t5_pri_con_w =~ 1*t5_pri_con_fs
t1_inf_sha_beh_w =~ 1*t1_inf_sha_beh_fs
t3_inf_sha_beh_w =~ 1*t3_inf_sha_beh_fs
t4_inf_sha_beh_w =~ 1*t4_inf_sha_beh_fs
t5_inf_sha_beh_w =~ 1*t5_inf_sha_beh_fs
t1_inf_sha_att_w =~ 1*t1_inf_sha_att_fs
t3_inf_sha_att_w =~ 1*t3_inf_sha_att_fs
t4_inf_sha_att_w =~ 1*t4_inf_sha_att_fs
t5_inf_sha_att_w =~ 1*t5_inf_sha_att_fs

# covariances
pri_con_b ~~ cor_b_1*inf_sha_att_b + cor_b_2*inf_sha_beh_b
inf_sha_att_b ~~ cor_b_3*inf_sha_beh_b
t1_pri_con_w ~~ cor_w_1*t1_inf_sha_att_w + cor_w_2*t1_inf_sha_beh_w
t1_inf_sha_att_w ~~ cor_w_3*t1_inf_sha_beh_w
t3_pri_con_w ~~ a*t3_inf_sha_att_w + b*t3_inf_sha_beh_w
t3_inf_sha_att_w ~~ c*t3_inf_sha_beh_w
t4_pri_con_w ~~ a*t4_inf_sha_att_w + b*t4_inf_sha_beh_w
t4_inf_sha_att_w ~~ c*t4_inf_sha_beh_w
t5_pri_con_w ~~ a*t5_inf_sha_att_w + b*t5_inf_sha_beh_w
t5_inf_sha_att_w ~~ c*t5_inf_sha_beh_w

# setting variances of observed variables to zero
t1_pri_con_fs ~~ 0*t1_pri_con_fs
t3_pri_con_fs ~~ 0*t3_pri_con_fs
t4_pri_con_fs ~~ 0*t4_pri_con_fs
t5_pri_con_fs ~~ 0*t5_pri_con_fs
t1_inf_sha_att_fs ~~ 0*t1_inf_sha_att_fs
t3_inf_sha_att_fs ~~ 0*t3_inf_sha_att_fs
t4_inf_sha_att_fs ~~ 0*t4_inf_sha_att_fs
t5_inf_sha_att_fs ~~ 0*t5_inf_sha_att_fs
t1_inf_sha_beh_fs ~~ 0*t1_inf_sha_beh_fs
t3_inf_sha_beh_fs ~~ 0*t3_inf_sha_beh_fs
t4_inf_sha_beh_fs ~~ 0*t4_inf_sha_beh_fs
t5_inf_sha_beh_fs ~~ 0*t5_inf_sha_beh_fs

# control variables
t1_pri_con_fs ~ age + edu_num + male
t3_pri_con_fs ~ age + edu_num + male
t4_pri_con_fs ~ age + edu_num + male
t5_pri_con_fs ~ age + edu_num + male
t1_inf_sha_beh_fs ~ age + edu_num + male
t3_inf_sha_beh_fs ~ age + edu_num + male
t4_inf_sha_beh_fs ~ age + edu_num + male
t5_inf_sha_beh_fs ~ age + edu_num + male
t1_inf_sha_att_fs ~ age + edu_num + male
t3_inf_sha_att_fs ~ age + edu_num + male
t4_inf_sha_att_fs ~ age + edu_num + male
t5_inf_sha_att_fs ~ age + edu_num + male
'
fit <- sem(model, data = d_wide_all, orthogonal = TRUE, missing = "ML")
summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
fit_riclpm_5w <- fit
```

The results show the same between person effects. Within-person effects disappear, which is understandable given the longer interval. Effects hence remain stable also across longer time intervals and until 2018.
